{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2025-01-10 Notebook LaTEX/Proposal/main.tex
>w<, changes

    \subsection{Future works for R-WAPG}
        There is one intriguing detail in the burried in the literatures but weren't realized in it. 
        It has the potential to include more variants of the FISTA algorithms and their convergence proof. 
        Our future works would be to extend the frameworks and weaken it further while retaining the goal of getting some type of upper bound on the value $F(x_k) - F^*$ and show that there are choices for the momentum parameter $\alpha_k$ such that convergence is possible. 
        \subsubsection{Nesterov's idea of strong convexity transfer}
        \todoinline{\noindent
            In terms of theories, it's possible to consider: 
            \begin{enumerate}
                \item Nesterov, 2013, ``Gradient methods for minimizing composite functions'', strong convexity transfer. 
                \item ``An introduction to continuous optimization for imaging'', Algorithm 5, the same thing is there as well. 
            \end{enumerate}
        }
        \subsubsection{Tying up some loose ends}
        \todoinline{\noindent
            In terms of practice, we missing convergence rate of Free-RWAPG, and the convergence of the norm of the gradient method for R-WAPG. 
        }

@@

            \begin{theorem}[Outer loop complexity under criterion C2]\label{theorem:catalyst2-outer-loop}
                For the iterates $(x_k)_{k \ge 0}$ generated by algorithm in Definition \ref{def:catalyst-relative}, we have 
                \begin{enumerate}
                    \item If $\mu > 0$, choose $\alpha_0 = \sqrt{q}$, $\delta_k = \sqrt{q}/(2 - \sqrt{q})$. 
                    Then the iterates $(x_k)_{k \ge 0}$ satisfies $F(x_k) - F^* \le \mathcal O\left(1 - \sqrt{q}/2\right)^k$. 
                    \item If $\mu = 0$, choose $\alpha_0 = 1$, $\delta_k = 1/(k + 1)^2$ satisfies $F(x_k) - F^* \le \mathcal O(k^{-2})$. 
                \end{enumerate}
            \end{theorem}
            \begin{remark}
                This is Proposition 8, 9 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018}.
                For a precise description of the upper bound, see Theorem 8. 
            \end{remark}
            The key improvement here compared to using absolute inexactness for $\mathbb M$ as stated by Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} is that $(\delta_k)_{k \ge0}$ doesn't require knowledge on $F^*$. 
            This innocent detail helps to develop a nonconvex variant of Catalyst call 4WD Catalyst which is the focus of the paper by Paquette \cite{paquette_catalyst_2018}. 
            Corollary 16 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018} gives complexity for $\mathbb M$ Using termination criterion C2 with a warm start specialized for $C2$. 
            It's important to note that the upper complexity bounds are much better, and it doesn't require bounded level set compared to Theorem \ref{prop:inner-loop-complexity-cnvx}.         
    \subsection{Potential future research}\label{ssec:catalyst-future}
        Now, we have enough context to understand the potential future directions of research regarding the Catalyst Acceleration framework. 
        \subsubsection{Necoara et al.'s comments on Catalyst Acceleration}

@@

>>>>

    \subsection{Future works for R-WAPG}
        There is one intriguing detail in the burried in the literatures but weren't realized in it. 
        It has the potential to include more variants of the FISTA algorithms and their convergence proof. 
        Our future works would be to extend the frameworks and weaken it further while retaining the goal of getting some type of upper bound on the value $F(x_k) - F^*$ and show that there are choices for the momentum parameter $\alpha_k$ such that convergence is possible. 
        \subsubsection{Nesterov's idea of strong convexity transfer}
            \todoinline{\noindent
                In terms of theories, it's possible to consider: 
                \begin{enumerate}
                    \item Nesterov, 2013, ``Gradient methods for minimizing composite functions'', strong convexity transfer. 
                    \item ``An introduction to continuous optimization for imaging'', Algorithm 5, the same thing is there as well. 
                \end{enumerate}
                In Nesterov's, take note of Algorithm: Accelerated Method (4.9) and the convergence claim: Theorem 6. 
            }
            We consider the case that $F = f + g$ where, $f$ is $L$ Lipschitz smooth, $\mu_f \ge 0$ strongly convex and $g$ is closed convex. 
            In Nesterov's 2013 paper \cite{nesterov_gradient_2013}, he consider accelerated  minimization problem $\phi = f + \Psi$ with $f$ $L_f$ smooth and $\Psi$ being $\mu_\Psi \ge 0$ strongly convex. 
            \par
            This detail on itself is not necessarily interesting, since without lost of generality, we can always do the splitting $f + \mu_\Psi/2 \Vert \cdot\Vert^2$ and $\Psi - \mu_\Psi/2\Vert \cdot\Vert^2$ instead so that the smooth part is $\mu_\Psi \ge 0$ strongly convex. 
            It's an interesting detail we should consider because: 
            \begin{enumerate}
                \item A strongly convex nonsmooth parts still gives linear convergence by Theorem 6 in Nesterov's 2013 \cite{nesterov_gradient_2013}. 
                \item The strong convexity constant can be easily estimated via a routine specified as (5.14) in Nesterov 2013 \cite{nesterov_gradient_2013} and the complexity of the estimation is bounded precisely. 
            \end{enumerate}
            (i) indicates that our theories of R-WAPG is incomplete, since it doesn't predict linear convergence when $g$ is strongly convex. 
            (ii) indicates that splitting the strongly convex objective so that it's with the proximal operator exposes computational advantage. 
            \par
            Furthermore, Nesterov was not the only person who thought about it.
            In 
            Chambolle, Pock \cite{chambolle_introduction_2016} Algorithm 5, several variants of the FISTA algorithm were captured together into one formulation, and it assumes that $F = f + g$ where $f, g$ has strong convexity index $\mu_f \ge 0, \mu_g \ge 0$, and $F$ is $\mu := \mu_f + \mu_g \ge 0$ strongly convex. 
            It's not trivial on how the R-WAPG framework can be modified to include strong convexity presenting in the nonsmooth part.

        % \subsubsection{Tying up some loose ends}
        %     \todoinline{\noindent
        %         In terms of practice, we are missing convergence rate of Free-RWAPG, and the convergence of the norm of the gradient method for R-WAPG. 
        %     }

@@

            \begin{theorem}[Outer loop complexity under criterion C2]\label{theorem:catalyst2-outer-loop}
                For the iterates $(x_k)_{k \ge 0}$ generated by algorithm in Definition \ref{def:catalyst-relative}, we have 
                    \item If $\mu > 0$, choose $\alpha_0 = \sqrt{q}$, $\delta_k = \sqrt{q}/(2 - \sqrt{q})$. 
                    Then the iterates $(x_k)_{k \ge 0}$ satisfies $F(x_k) - F^* \le \mathcal O\left(1 - \sqrt{q}/2\right)^k$. 
                    \item If $\mu = 0$, choose $\alpha_0 = 1$, $\delta_k = 1/(k + 1)^2$ satisfies $F(x_k) - F^* \le \mathcal O(k^{-2})$. 
                This is Proposition 8, 9 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018}.
                For a precise description of the upper bound, see Theorem 8. 
            The key improvement here compared to using absolute inexactness for $\mathbb M$ as stated by Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} is that $(\delta_k)_{k \ge0}$ doesn't require knowledge on $F^*$. 
            This innocent detail helps to develop a nonconvex variant of Catalyst call 4WD Catalyst which is the focus of the paper by Paquette \cite{paquette_catalyst_2018}. 
            Corollary 16 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018} gives complexity for $\mathbb M$ Using termination criterion C2 with a warm start specialized for $C2$. 
            It's important to note that the upper complexity bounds are much better, and it doesn't require bounded level set compared to Theorem \ref{prop:inner-loop-complexity-cnvx}.         
    \subsection{Potential future research}\label{ssec:catalyst-future}
        Now, we have enough context to understand the potential future directions of research regarding the Catalyst Acceleration framework. 
        \subsubsection{Necoara et al.'s comments on Catalyst Acceleration}
            Necoara et al. \cite{necoara_linear_2019} considered optimization problem $f^* = \min_{x \in X} f(x)$ with $f: X \subseteq \RR^n \rightarrow \RR$ and $X$ closed and convex. 
            They extended the linear convergence results of accelerated gradient method such as Nesterov's acceleration with proximal gradient into a wider setting than strong convexity. 
            As a secondary objective, they introduced and stated the relations between several weakened characterizations of strong convexity on a closed convex set. 
            Definition 1, 2, 3, 4, 5, introduced the ideas of: Quasi-strong convexity, Quadratic under approximation, Quadratic gradient growth, quadratic functional growth (recall that it was stated as a consequence of strong convexity in Lemma \ref{lemma:q-growth}), and Global error bound conditions. 
            The content of their paper is very in-depth hence for our interests, we focus on their comments on the first Catalyst paper by Lin et al. \cite{lin_universal_2015}. 
            They said, and here we quote: 
            \begin{quote}
                It is also worth to investigate the complexity bounds obtained when wrapping linearly-convergent algorithms under the proposed conditions in an outer-loop using a generic acceleration scheme such as Catalyst \cite{lin_universal_2015}. This would allow to extend to non-strongly convex settings a wide range of incremental optimization algorithms designed for large finite-sum problems arising in machine learning and statistics.
            \end{quote}
            We note that, their idea of extension can be applied to inner loop $\mathbb M$, or out loop $\mathbb A$, either, or both. 

@@

            One intriguingly detail in the Catalyst framework eluded us. 
            It may not be obvious to the readers, so we shall elucidate. 
            The concern starts by considering the necessary assumption in VRMs. 
            Defazio et al.\cite{defazio_saga_2014} SAGA, Finito et al. \cite{defazio_finito_2014} requires Lipschitz continuous gradient on each individual $f_i$ in the objective function $F = \sum_{i = 1}^n f_i$. 
            Schimdt et al. \cite{schmidt_minimizing_2017} also requires Lipscthiz smoothness for the non-smooth part of a composite objective. 
            Xiao, Zhang, SVRG \cite{xiao_proximal_2014} requires Lipscthiz gradient assumption as well. 
            This seemingly raises a crucial question: ``Where does the Lipschitz continuous gradient of the smooth part make its presence in the Catalyst Framework?''

### 2025-01-10 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

    \todo{Write this abstract when finishing. }
\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
\noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
\section{Introduction}
    Suppose we are minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$ for simplicity. 
    Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$. 
    \par 
    A good choice of a minimization algorithm is the Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983}. 
    Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
    \begin{align}
        & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
        \\
        & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
        \\
        & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
        \\
        & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
    \end{align}\label{eqn:example_algorithm}
    It's well known that if the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, faster than the gradient descent method which is $\mathcal O(1/k)$, and it's optimal.
    See Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018}. 
    However, everything is not sunshine and rainbow because the above scheme is associated with an issue. 
    When $F$ is $\mu > 0$ strongly convex, the optimality gap $F(x_k) - F(x^*)$ oscillates and converges sub-linearly, making it worse than gradient descent. See page 9 of Su et al. \cite{su_differential_2016}. 
    \par
    This issue motivated a vast amount of literatures aims at improving, interpreting, and extending this method. 
    Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
    Beck and Teboulle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it has an $\mathcal O(1/k^2)$ convergence still, but it performs empirically better. 
    See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm. 
    \par
    Inspired by prior works and the method of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, we present to you firstly, an alternative to restarting that performs well empirically. 
    Secondly, a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 
    The R-WAPG has a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(\theta_k)_{k \ge 1}$. 
    It also has descriptive power to describe several variants of FISTA in the literatures.

    \subsection{Contributions}
        Our contributions are two folds, theoretical and practical. 
        Our results are based the assumption $F = f + g$ where $g:\RR^n \rightarrow \overline\RR$ is convex proper and closed, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
        Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
        The choices for $\theta_k$ varies for different variants of the accelerated proximal gradient algorithm. 
        In Chambolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space. 
        In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergence rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $F$. 
        V-FISTA has $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$. 
        We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example_algorithm} and showed an upper bound of the optimal gap. 
        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
            \alpha_0 &\in (0, 1], 
            \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
            \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
            \mathcal O\left(
        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}. 
        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
        In Theorem \ref{thm:fixed-momentum-fista}, it demonstrates that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex. 
        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}). 
        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ with minimal computational cost. 
        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart. 
    \subsection{Prior works}
            The prior works' section is too little, it requires some expansion in the future for sure.
        One of the most relevant works is by 
        \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them.}{\hl{Apidopoulos et al. }\cite{apidopoulos_convergence_2018}}. 
        They showed that a relaxed choice of the sequence that doesn't strictly follow the Nesterov's rule still leads to the convergence of the momentum algorithm. 
        \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them. }{See Attouch, et al. \cite{attouch_first-order_2022}, Maulen and Peypouquet \cite{maulen_speed_2023}} 
        and references within for the idea of Hessian Damping for stabilizing the Nesterov's accelerated gradient without/with restarting.

>>>>

    \todo{Write this abstract when finishing. }
\end{abstract}
\todo{Remember to update these subject classificiations. }
{
    \noindent{\bfseries 2010 Mathematics Subject Classification:}
    Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
    \noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
}
\section{Introduction}
    Suppose we are minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$ for simplicity. 
    Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$. 
    \par 
    A good choice of a minimization algorithm is the Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983}. 
    Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
    \begin{align}
        & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
        \\
        & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
        \\
        & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
        \\
        & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
    \end{align}\label{eqn:example_algorithm}
    It's well known that if the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, faster than the gradient descent method which is $\mathcal O(1/k)$, and it's optimal.
    See Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018}. 
    However, everything is not sunshine and rainbow because the above scheme is associated with an issue. 
    When $F$ is $\mu > 0$ strongly convex, the optimality gap $F(x_k) - F(x^*)$ oscillates and converges sub-linearly, making it worse than gradient descent. See page 9 of Su et al. \cite{su_differential_2016}. 
    \par
    This issue motivated a vast amount of literatures aims at improving, interpreting, and extending this method. 
    Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
    Beck and Teboulle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it has an $\mathcal O(1/k^2)$ convergence still, but it performs empirically better. 
    See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm. 
    \par
    Inspired by prior works and the method of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, we present to you firstly, an alternative to restarting that performs well empirically. 
    Secondly, a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 
    The R-WAPG has a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(\theta_k)_{k \ge 1}$. 
    It also has descriptive power to describe several variants of FISTA in the literatures.

    \subsection{Contributions}
        Our contributions are two folds, theoretical and practical. 
        Our results are based the assumption $F = f + g$ where $g:\RR^n \rightarrow \overline\RR$ is convex proper and closed, and $f$ is an $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
        \par
        Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
        The choices for $\theta_k$ varies for different variants of the accelerated proximal gradient algorithm. 
        In Chambolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ which gives weak convergence of the iterates $x_k$ in Hilbert space. 
        In Chapter 10 of Beck's Book \cite{beck_first-order_2017}, a variant called V-FISTA can achieve the faster linear convergence rate: $\mathcal O((1 - \sqrt{\mu/L})^k)$ on the optimality gap for $\mu > 0$ strongly convex $F$. 
        V-FISTA has $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$. 
        \par
        We relax the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example_algorithm} and showed an upper bound of the optimal gap. 
        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
        \begin{align*}
            \alpha_0 &\in (0, 1], 
            \\
            \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
            \\
            \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
        \end{align*}
        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
        \begin{align*}
            \mathcal O\left(
                \left(
                    \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
                \right)
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right). 
        \end{align*}
        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces to a variant of FISTA proposed in Chambolle, Dossal \cite{chambolle_convergence_2015}, and we are able to show the same convergence rate in Theorem \ref{thm:r-wapg-on-cham-doss}. 
        When $\rho_k = 1, \mu = 0$, R-WAPG reduces perfectly to FISTA by Beck \cite{beck_first-order_2017}, if $\mu > 0, \rho_k = 1$, it reduces to the V-FISTA by Beck \cite{beck_first-order_2017}. 
        In Theorem \ref{thm:fixed-momentum-fista}, it demonstrates that R-WAPG frameworks gives a linear convergence claim for all fixed momentum method where $\alpha_k := \alpha \in (\mu/L, 1)$ and  $F$ is $\mu > 0$ strongly convex. 
        \par
        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG'' (See Algorithm \ref{alg:free-rwapg}). 
        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ with minimal computational cost. 
        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart. 
    \subsection{Prior works}
        \todoinline{\noindent
            The prior works' section is too little, it requires some expansion in the future for sure.
            \begin{enumerate}
                \item Paper: ``An introduction to continuous optimization for imaging'', Chambolle, Pock. 
            \end{enumerate}

        }
        One of the most relevant works is by 
        \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them.}{\hl{Apidopoulos et al. }\cite{apidopoulos_convergence_2018}}. 
        They showed that a relaxed choice of the sequence that doesn't strictly follow the Nesterov's rule still leads to the convergence of the momentum algorithm. 
        \par 
        \todo{$\blacksquare$ Add them \\ $\blacksquare$ Cite them. }{See Attouch, et al. \cite{attouch_first-order_2022}, Maulen and Peypouquet \cite{maulen_speed_2023}} 
        and references within for the idea of Hessian Damping for stabilizing the Nesterov's accelerated gradient without/with restarting.
